Output Summary

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Update how upper triangle of rho_mat is excluded
From MCMC diagnostics

# discard duplicate correlation terms: all rho parameters for a given process are equal
all_rho = match_params(post, "^rho")
rho_keep = match_params(post, "^rho_.+[2,1")
rho_discard = all_rho[!(all_rho %in% rho_keep)]
diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
```

>>>>

# discard any node that simply track prior densities, no need to MCMC diagnose them
pr_rm = c(match_params(diag_post, "_pr["), match_params(diag_post, "_pr$"))
diag_post = suppressMessages(post_remove(diag_post, pr_rm, ask = FALSE))
```

```{r discard-rho-upper-tri}
# duplicate correlation parameters do not need to have MCMC diagnostics ran
# those on the diagonal have already been discarded 
# this code discards those in the upper triangle 
rho_params = match_params(diag_post, "rho", type = "base_only")
rho_keep = unlist(lapply(rho_params, function(x) paste0(x, vcov_inds)))
all_rho = match_params(diag_post, "^rho", type = "base_index")
rho_discard = all_rho[!(all_rho %in% rho_keep)]
diag_post = suppressMessages(post_remove(diag_post, rho_discard, ask = FALSE))
```
